### 2020-08-28 LaTeX/sections/paper.tex
Paper- Changed the tables and the texts related to estimategas completely

@@

At the time of this writing, Ethereum transaction receipts only contain the net gas consumption and not the total gas consumption (total gas consumption is defined as $gas refunded + gasUsed$) and we cannot obtain the value of the EVM's refund counter from inside the EVM. So in order to account for refunds inside each priority queue smart contract, we can calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing the highest priority elements and then we multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQUnitTests}).

Another way to obtain the amount of refund in each priority queue is to use the \texttt{estimateGas API} which provides a rough idea about the total amount of gas that is required for a transaction to go through. The \texttt{web3.eth.estimateGas} pretends the transaction is included in the block and its functions (with the parameters passed) will be executed on the Ethereum blockchain. Doing so, it provides us an estimate of how much gas is needed to be sent with the transaction. The third and fourth columns of Table~\ref{tab:PQUnitTests}) show the total amount of gas required for dequeuing 50 integers from each priority queue (provided by estimateGas) and the amount of gas refund ($Total Gas Consumption - gasUsed$) respectively.

Note that in order to urge miners to process smart contract with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}. So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller. For example, the amount of gas that has been used when dequeuing 50 integers from the linked list with mapping priority queue is 731,514 and since $3,000,000 > 731,514/2$, the amount of refund returned to the caller is $731,514/2 = 365,757$.

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
% A little explanation on gas metrics (Mahsa: please let me know if this is still unclear:)

@@

% +++++++++++++%
% so in our case, let's take the first row of the above table:

%The transaction consumes 2,518,131 gas
%The gas limit is set up at  11,741,495
%Firstly, they sender get back (11,741,495 - 2,518,13) = 9,223,364 units of unused gas.
%However, the amount of gas that has been used in the contract is 2,518,131 and since 9,223,364 >2,518,131/2, the REFUND generated will be 2,518,131/2= 1,259,065.
%
%The total gas cost of transaction estimated by estimateGas is 3,283,480 
%estimateGas - gasUsed = gasRefund => 3,283,480 - 2,518,131 = 765,349
%
%So we can argue that the estimateGas() gives us an approximate total cost of the transaction and it contains the capped refund counter.

% error in estimateGas:  
%   https://ethereum.stackexchange.com/questions/266/what-are-the-limitations-to-estimategas-and-when-would-its-estimate-be-considera
%   https://github.com/trufflesuite/ganache-core/issues/26

%from solidity readdocs: estimateGas Will call estimate the gas a method execution will take when executed in the EVM without. The estimation can differ from the actual gas used when later sending a transaction, as the state of the smart contract can be different at that time.
% estimateGas works by pretending the transaction was actually being included in the blockchain, and then returning the exact gas amount that would have been charged if that pretend operation was real. In other words, it uses the exact same procedure a miner would use to calculate the actual fee.
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %

@@

\subsubsection*{Linked List.} Removing the highest priority element from the list can be done in two ways. We can use the \texttt{self-destruct()} operation to destroy the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract). Although the \texttt{self-destruct()} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller. Another design perspective is to only update the head pointer of the linked list and leave the previous head (\ie smart contract) on Ethereum blockchain when removing the highest priority element from the list. Although the first technique is a bit more costly (because it adds an extra operation \texttt{self-destruct()} to the \texttt{dequeue()} function), it results the in the less final net cost due to the 24000 gas refunds. Also, it is best to avoid storing unnecessary storage variables on chain. Table~\ref{tab:LLvsLLMapping} outlines different gas metrics for iteratively dequeuing the highest priority element from the two implementations of sorted linked lists that contain 50 unsigned integers.

@@

\subsubsection*{Linked List with Mapping.} Similarly, linked list with mapping can be implemented in two ways. For dequeuing items from this priority queue we can use the \texttt{delete()} method and remove the mapping element that contains the highest priority item from storage completely  \textbf{and} update the head and tail pointers of the list. Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) and costs in 5000 gas. So although the \texttt{delete()} method refunds in 15000 gas~\cite{wood2014ethereum}, it is yet a gas-costly operation  as it increases the overall gas cost of the transaction. In another technique, we can only update the head and tail pointers of the linked list when dequeueing the highest priority items and not delete the mapping element associated with the previous pointers. As it can be seen in Table~\ref{tab:LLvsLLMapping}, this scheme consumes less gas to dequeue 50 unsigned integers from this priority queue with respect to the previous technique where we clear up the chain, however, leaving unnecessary storage data on chain is not a proper design practice.

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\begin{table}[]
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
                                                                						& with \texttt{Self-destruct()} 		& without \texttt{Self-destruct()}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %

@@

Based on Table~\ref{tab:LLvsLLMapping}, the linked list with \texttt{Self-destruct()} appears to be a good candidate for the call market implementation. However, as it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into this priority queue is significantly greater than the linked list with mapping as insertion is identical to creating new contracts. Accordingly, we choose to implement the call market with the linked list with mapping that uses the  the \texttt{delete()} method to clear up the chain every time the highest priority element is removed from the list. In overall this priority queue introduces a moderate gas cost for both insertion (\ie order submission) and removal (\ie matching the orders).

@@

Table~\ref{tab:worst_case_matching} outlines the \texttt{Match()} function's computational costs and performance for three different implementations of the call market. We used three different designs of the linked list with mapping priority queue. (1) Every time a trade happens, we use the \texttt{delete()} method to remove the mapping elements that contains best bid and ask orders item from storage completely \textbf{and} update the head and tail pointers of the list. (2) We only update the pointers of the priority queue and do not remove the best bid and ask orders during the entire matching process. Instead we destroy the priority queue smart contract~\footnote{We execute a public function defined in the priority queue smart contract which itself calls the \texttt{self-destruct()} operation and transfers its funds (if any) to the call market contract.} once the matching is completed. (3) In the last implementation, we allow the matching process to be completed and do not clear any on chain data. As it can be seen in Table~\ref{tab:worst_case_matching}, the \texttt{Match()} operatin shows a better performance when killing the priority contract and/or not clearing data from the chain. Although deleting the priority queue contract adds an extra external call to the \texttt{Match()} function and should technically increase the gas cost, the 24000 gas refunds from \texttt{selfdestruct()} would compensate the cost. So it can still match as same number of orders (before running out of gas)as in the no on chain clearing implementation. The last column of Table~\ref{tab:worst_case_matching} reflects the gas cost for matching 1000 pairs of bids and asks for which we set the block gas limit to the maximum of  $2^{53}$ (the Javascript's max safe integer).

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{Clearing the Mapping Elements}}         			& 38 pairs                					& 5,372,679                   				& 457,326,935                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{Deleting the Priority Queue Contract}}           	& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{No On-chain Clearing}} 		                       	& 210 pairs							& 5,299,877							& 25,095,370				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %

@@

%---------+++++++++++++++++++-----------------
\subsection {Linkedlist}
Every time a trade happens, we use the \texttt{self-destruct} operation to remove the nodes (\ie smart contracts) containing the best bid and ask orders from the Ethereum blockchain. When a node is deleted, it transfers its funds (if any) to the payable address of the CallMarket contract that has been previously passed to it as a constructor argument. Also, removing a smart contract from the Ethereum blockchain refunds 24000 gas to the caller.

@@

>>>>

\begin{table}[]
\centering
\begin{tabular}{|c|c|c|}
\hline

\textbf{\thead{Priority Queue}}    & \textbf{\thead{Net Cost in Gas\\ (\texttt{gasUsed})}}             & \textbf{\thead{Gas Refunds from Deleting a Storage\\(Manually Calculated)}} \\ \hline

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Dynamic Array}}         				& 2,518,131            		      & 750,000                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Heap with \\ Static Array}}           				& 1,385,307                             & 750,000                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Mapping with \\ keys stored \\ in Heap}} 		& 2,781,684                            & 1,500,000                     \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{Linked List}                       							& 557,085               	           & 1,200,000                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %
	\textbf{\thead{Linked List with \\ Mapping}}          				& 731,514              	     	  &  3,765,000                       \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = %

@@

At the time of this writing, Ethereum transaction receipts only contain the net gas consumption (\texttt{gasUsed}) and we cannot obtain the value of the EVM's refund counter from inside the EVM~\cite{signer2018gas}. So in order to account for refunds inside each priority queue smart contract we calculate them manually; first we figure out exactly how much storage is being cleared when dequeuing the highest priority elements (\texttt{SSTORE} instruction) and then we multiply the number of storage slots cleared by 15,000 (see the last column of Table~\ref{tab:PQUnitTests}).

Note that in order to urge miners to process smart contracts with refunds, the accumulated gas refund can never exceed half the gas used up during computation~\cite{wood2014ethereum}. So at the end of a successful transaction, the amount of gas in the refund counter (capped at half the net gas used) is returned to the caller. Let's take a closer look at the last row of Table~\ref{tab:PQUnitTests}; gas that has been used for dequeuing 50 integers from the linked list with mapping priority queue is 731,514 and the gas limit has been set up to 11,741,495. Firstly, the caller will receive $(11,741,495 - 731,514) = 11,009,981$ units of unused gas. Also, the amount of refund we manually calculated based on the storage deletions is 3,765,000, and since this number is greater than half of he amount of gas that has been used in the contract ($3,765,000 > 731,514/2$), the refund generated will be $731,514/2 = 365,757$. So the caller of this transaction will eventually receive is $11,009,981 + 365,757 = 11,375,738$ units of gas.

%& \textbf{\thead{Net Cost\\in Gas\\ (\texttt{gasUsed})}}  
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
% A little explanation on gas metrics (Mahsa: please let me know if this is still unclear:)

@@

@@

\subsubsection*{Linked List.} Removing the highest priority element from the list can be done in two ways. We can use the \texttt{SELFDESTRUCT} operation to destroy the head node of the list (\ie smart contract) from the Ethereum blockchain and transfer its funds (if any) to a payable address (\eg the current block miner or the call market contract). Although the \texttt{SELFDESTRUCT} operation does not remove the initial byte code of the contract from the chain, but it frees up the state storage and refunds 24000 gas to the caller. Another design perspective is to only update the head pointer of the linked list and leave the previous head (\ie smart contract) on Ethereum blockchain when removing the highest priority element from the list. Although the first technique is a bit more costly (because it adds an extra operation \texttt{SELFDESTRUCT} to the \texttt{dequeue()} function), it results the in the less final net cost due to the 24000 gas refunds. Also, it is best to avoid storing unnecessary storage variables on chain. Table~\ref{tab:LLvsLLMapping} outlines different gas metrics for iteratively dequeuing the highest priority element from the two implementations of sorted linked lists that contain 50 unsigned integers.

@@

\subsubsection*{Linked List with Mapping.} Similarly, linked list with mapping can be implemented in two ways. For dequeuing items from this priority queue we can use the \texttt{DELETE} method and remove the mapping element that contains the highest priority item from storage completely  \textbf{and} update the head and tail pointers of the list. Deleting a storage variable is identical to setting a non-zero variable to zero (\texttt{SSTORE} 0) that costs 20,000 gas but with15,000 refunded~\cite{wood2014ethereum}. So although the \texttt{DELETE} method refunds in 15000 gas, it is yet a gas-costly operation  as it increases the overall gas cost of the transaction. In another technique, we can only update the head and tail pointers of the linked list when dequeueing the highest priority items and not delete the mapping element associated with the previous pointers. As it can be seen in Table~\ref{tab:LLvsLLMapping}, this scheme consumes less gas to dequeue 50 unsigned integers from this priority queue with respect to the previous technique where we clear up the chain, however, leaving unnecessary storage data on chain is not a proper design practice.

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\begin{table}[]
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Gas Metrics}}                        							& \multicolumn{2}{c|}{\textbf{Linked List}}           						& \multicolumn{2}{c|}{\textbf{Linked List with Mapping}}     					\\ \cline{2-5} 
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
                                                                								& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{DELETE} 		& without \texttt{DELETE}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
                  \textbf{\thead{Net Cost in Gas\\(\texttt{gasUsed})}}                        				& 557,085                    			& 721,370                     			& 731,514                     		& 334,689                      				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
 \textbf{\thead{Gas Refund \\from Deleting a Storage\\(Manually Calculated)}}            & 1,200,000                 				& 0                      					& 3,765,000                    		& 765,000                       				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %

@@

Based on Table~\ref{tab:LLvsLLMapping}, the linked list with \texttt{SELFDESTRUCT} appears to be a good candidate for the call market implementation. However, as it can be seen in Figure~\ref{fig:random_insertion}, the associated cost for inserting elements into this priority queue is significantly greater than the linked list with mapping as insertion is identical to creating new contracts. Accordingly, we choose to implement the call market with the linked list with mapping that uses the  the \texttt{DELETE} method to clear up the chain every time the highest priority element is removed from the list. In overall this priority queue introduces a moderate gas cost for both insertion (\ie order submission) and removal (\ie matching the orders).

@@

Table~\ref{tab:worst_case_matching} outlines the \texttt{Match()} function's computational costs and performance for three different implementations of the call market. We used three different designs of the linked list with mapping priority queue. (1) Every time a trade happens, we use the \texttt{DELETE} method to remove the mapping elements that contains best bid and ask orders from storage completely \textbf{and} update the head and tail pointers of the list. (2) We only update the pointers of the priority queue and do not remove the best bid and ask orders during the entire matching process. Instead we destroy the priority queue smart contract~\footnote{We execute a public function defined in the priority queue smart contract which itself calls the \texttt{self-destruct()} operation and transfers its funds (if any) to the call market contract.} once the matching is completed. (3) In the last implementation, we allow the matching process to be completed and do not clear any on chain data. As it can be seen in Table~\ref{tab:worst_case_matching}, the \texttt{Match()} operation shows a better performance when killing the priority contract and/or not clearing data from the chain. Although deleting the priority queue contract adds an extra external call to the \texttt{Match()} function and should technically increase the gas cost, the 24000 gas refunds from \texttt{SELFDESTRUCT} would compensate the cost. So it can still match as same number of orders (before running out of gas)as in the no on chain clearing implementation. The last column of Table~\ref{tab:worst_case_matching} reflects the gas cost for matching 1000 pairs of bids and asks for which we set the block gas limit to the maximum of  $2^{53}$ (the Javascript's max safe integer).

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{Clearing the Mapping Elements}}         			& 38 pairs                					& 5,372,679                   				& 457,326,935                      \\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{Destroying the Priority Queue Contract}}           	& 210 pairs	                     				& 5,304,211 							& 25,099,713				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %
	\textbf{\thead{No On-chain Clearing}} 		                       	& 210 pairs							& 5,299,877							& 25,095,370				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = = = = = = = %

@@

%---------+++++++++++++++++++-----------------
\subsection {Linkedlist}
Every time a trade happens, we use the \texttt{SELFDESTRUCT} operation to remove the nodes (\ie smart contracts) containing the best bid and ask orders from the Ethereum blockchain. When a node is deleted, it transfers its funds (if any) to the payable address of the CallMarket contract that has been previously passed to it as a constructor argument. Also, removing a smart contract from the Ethereum blockchain refunds 24000 gas to the caller.

@@

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
%The tables I changed after estimateGas, Not sure which ones to keep. Should talk to Jeremy

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  %
\begin{table}[]
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{Gas Metrics}                        							& \multicolumn{2}{c|}{Linked List}           						& \multicolumn{2}{c|}{Linked List with Mapping}     					\\ \cline{2-5} 
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
                                                                						& with \texttt{SELFDESTRUCT} 		& without \texttt{SELFDESTRUCT}                	& with \texttt{delete} 		& without \texttt{delete}              		\\ \hline                                                                                                                                                                                                                                                          % = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
                   Net Cost in Gas                          					& 557,085                    			& 721,370                     				& 731,514                     	& 334,689                      				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
\thead{Total Cost in Gas \\ (from \texttt{estimateGas})} 		& 1,772,085                  			& 736,370                  					& 3,731,514                     	& 1,099,689                       				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
		    The Difference                                             		& 1,215,000                  			& 15,000                      				& 3,000,000                    	& 765,000                       				\\ \hline
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = = = = = = = = = = =  = = = = = =  = = = = = = %
